---
title: "p8105_hw5_gw2383"
author: "Guojing Wu"
date: "2018/11/3"
# output: html_document
output:
  github_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)

theme_set(theme_bw())
```

## Problem 1

###Create a tidy dataframe containing data from all participants

```{r}
exp_df = 
  tibble(file_name = list.files("./data/problem1/", pattern = "*")) %>% 
  mutate(data = map(.x = str_c("./data/problem1/", file_name, sep=""), ~ read.csv(.x))) %>% # read data
  separate(file_name, into = c("filename", "postfix"), sep = "\\.") %>% 
  select(-postfix) %>% # remove postfix
  separate(filename, into = c("group", "id"), sep = "_", remove = F) %>% 
  unnest() %>% 
  gather(key = weeks, value = observation, week_1:week_8) %>% # gathering, tidy the data
  separate(weeks, into = c("prefix", "weeks"), sep = "_") %>% 
  select(-prefix) %>% # remove prefix
  mutate(
    filename = factor(filename), 
    group = factor(group, levels = c("exp", "con")), 
    id = factor(id), 
    weeks = factor(weeks)
  ) # transfer to factor

exp_df
```

### a spaghetti plot showing observations on each subject over time

```{r, dpi = 300, out.width = "80%"}
exp_df %>% 
  ggplot(aes(x = weeks, y = observation, group = filename, col = group)) +
  geom_line()
```

In this plot we can see the observations in `exp` group are higher than observations in `con` group in general (p.value = `r t.test(observation ~ group, data = exp_df, alternative = "greater")$p.value`).

## Problem 2

### Describe the raw data

```{r}
homi_df = 
  read.csv("./data/problem2/homicide-data.csv") %>% 
  janitor::clean_names() %>% 
  mutate(city_state = paste(city, state, sep = ", "))
```

So in this dataset we have `r dim(homi_df)[1]` observations, and `r dim(homi_df)[2]` variables include: `r colnames(homi_df)`

The total number of homicides and the number of unsolved homicides within cities are listed below:

```{r}
homi_stat = 
  homi_df %>% 
  group_by(city_state) %>% 
  summarise(
    unsolved = sum(disposition %in% c("Closed without arrest", "Open/No arrest")), 
    total_number = n()
    )

knitr::kable(homi_stat)
```

We noticed there is one row really strange: 
`r homi_stat %>% filter(min_rank(total_number) == 1) %>%  knitr::kable()`
But there doesn't seem to have a good explanation so we'll just leave it there.

### For the city of Baltimore, MD, use the `prop.test` function to estimate the proportion of homicides that are unsolved

```{r}
# a function that doing the prop.test for homi_stat
city_pt = function(df) {
  prop.test(x = df$unsolved, n = df$total_number) %>% 
    broom::tidy()
}

output = 
  homi_stat %>% 
  filter(city_state == "Baltimore, MD") %>% 
  city_pt()

output %>% 
  select(estimate, conf.low, conf.high) %>% 
  knitr::kable()
```

### run `prop.test` for each of the cities

```{r}
output_all = 
  homi_stat %>% 
  nest(unsolved, total_number) %>% 
  mutate(prop_test = map(.x = data, ~city_pt(.x))) %>% 
  unnest() %>% 
  select(city_state, estimate, conf.low, conf.high)

head(output_all,10)
```

Create a plot that shows the estimates and CIs for each city

```{r, dpi = 300, out.width = "100%"}
output_all %>% 
  ggplot(aes(x = reorder(city_state, estimate), y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  labs(x = "city") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

